### 2022-03-21 src/text/2-package-subsections/stats.tex
First addition

>>>>

In Gammapy, the fit statistics are log-likelihood functions normalized like chi-squares,
i.e. they follow the expression $2 \times log L$, where $L$ is the likelihood function used.
To account for the event nature of gamma-ray data, the likelihood functions implemented
in Gammapy for Poisson distribution the Cash
